---
title: "Assessment3"
author: "https://github.com/VictoriaUniversity-AU/assessment-1-Cathy-2022.git"
date: '2022-09-13'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
library(tidymodels)
library(caret)
#install.packages("factoextra")
library(factoextra)
#install.packages("ClusterR")
library(ClusterR)
```
### Task2: Import dataset, find out missing data and deal with missing data
#### Import dataset and fill the blank sell with NA
```{r}
future <- read.csv("future_500_team01.csv", na.strings = c(""))
str(future)
```
#### View missing data and create missing dataset
```{r}
sum(is.na(future))
view(colSums(is.na(future)))
missingdata <- future[!complete.cases(future),]
```
#### Deal with missing data of column State, assign value according to data of future or external sources
```{r}
future %>% filter(City=="New York")
future[is.na(future$State) & future$City=="New York","State"] <- "NY"
future[is.na(future$State) & future$City=="San Francisco","State"] <- "CA"
future[is.na(future$State) & future$City=="San Francisco","State"] <- "CA"
sum(is.na(future$State))
```
#### Deal with missing data, use median value to replace null data
```{r}
profit_median <- median(future$Profit, na.rm = TRUE)
future[is.na(future$Profit),"Profit"] <- profit_median
sum(is.na(future$Profit))

future <- future %>%  mutate(
  revenue_num = parse_number(Revenue),
  expenses_num = parse_number(Expenses),
  growth_num = parse_number(Growth)/100
  )

revenue_median <- median(future$revenue_num, na.rm = TRUE)
future[is.na(future$revenue_num),"revenue_num"] <- revenue_median
sum(is.na(future$revenue_num))

expenses_median <- median(future$expenses_num, na.rm = TRUE)
future[is.na(future$expenses_num),"expenses_num"] <- expenses_median
sum(is.na(future$expenses_num))

growth_median <- median(future$growth_num, na.rm = TRUE)
future[is.na(future$growth_num),"growth_num"] <- growth_median
sum(is.na(future$growth_num))

employee_median <- median(future$Employees, na.rm = TRUE)
future[is.na(future$Employees),"Employees"] <- employee_median
```
#### Dealing with outliers, finding posible dependent and independent value
```{r}
future_lin <- future %>% select(Employees, Profit, revenue_num, expenses_num, growth_num)
sum(is.na(future_lin))
boxplot(future_lin)
boxplot.stats(future_lin$Profit)
boxplot.stats(future_lin$revenue_num)

future_lin <- future_lin %>% filter(Profit<16000000) %>% 
  filter(revenue_num<19000000 & revenue_num>2000000)
boxplot(future_lin)

plot(future_lin)
scatter.smooth(x=future_lin$revenue_num, y=future_lin$Profit)
scatter.smooth(x=future_lin$expenses_num, y=future_lin$Profit)
scatter.smooth(x=future_lin$Profit, y=future_lin$growth_num)

```
# Build linear regression models
```{r}
set.seed(1000)
sub_future_lin <- future_lin %>% select(Profit, revenue_num, expenses_num)
InTrain <- createDataPartition(future_lin$Profit,p=0.8, list = FALSE)
Train_future <- sub_future_lin[InTrain,]
Test_future <- sub_future_lin[-InTrain,]

Train_future
Test_future
Model <- lm(Profit ~ ., data = Train_future) 
summary(Model)
```
### Predicton result:revenue_num and expenses_num infulence linear regression equation most
```{r}
predict_future <- predict(Model, Test_future)
predict_future
plot(predict_future, type="l", lty=1.8, col="blue")

```
### Task4: Data Clustering
#### Import dataset and figure out missing data
```{r}
mobile <- read.csv("mobile_phone_usage_team01.csv", na.strings = c(""))
str(mobile)
sum(is.na(mobile))
mobile_miss <- mobile[!complete.cases(mobile),]
```
#### Clean data, using median value or "0" to replace null data
```{r}
battery_power_median <- median(mobile$battery_power, na.rm = TRUE)
mobile[is.na(mobile$battery_power),"battery_power"] <- battery_power_median

mobile[is.na(mobile$blue), "blue"] <- 0

clock_speed_median <- median(mobile$clock_speed, na.rm = TRUE)
mobile[is.na(mobile$clock_speed),"clock_speed"] <- clock_speed_median
mobile[is.na(mobile$dual_sim), "dual_sim"] <- 0
mobile[is.na(mobile$fc), "fc"] <- 0
mobile[is.na(mobile$four_g), "four_g"] <- 0

int_memory_median <- median(mobile$int_memory, na.rm = TRUE)
mobile[is.na(mobile$int_memory),"int_memory"] <- int_memory_median

m_dep_median <- median(mobile$m_dep, na.rm = TRUE)
mobile[is.na(mobile$m_dep),"m_dep"] <- m_dep_median 

mobile_wt_median <- median(mobile$mobile_wt, na.rm = TRUE)
mobile[is.na(mobile$mobile_wt),"mobile_wt"] <- mobile_wt_median
mobile[is.na(mobile$n_cores), "n_cores"] <- 1
mobile[is.na(mobile$pc), "pc"] <- 0

px_height_median <- median(mobile$px_height, na.rm = TRUE)
mobile[is.na(mobile$px_height),"px_height"] <- px_height_median 
px_width_median <- median(mobile$px_width, na.rm = TRUE)
mobile[is.na(mobile$px_width),"px_width"] <- px_width_median
ram_median <- median(mobile$ram, na.rm = TRUE)
mobile[is.na(mobile$ram),"ram"] <- ram_median
sch_median <- median(mobile$sc_h, na.rm = TRUE)
mobile[is.na(mobile$sc_h),"sc_h"] <- sch_median

sum(is.na(mobile))

```
#### Detecting and deal with outliers
```{r}
boxplot(mobile)
boxplot.stats(mobile$px_width)
```

#### K-Mean clustering in the dataset and visualize the cluster
```{r}
mobile_scale <- scale(mobile)
opt_mobile=Optimal_Clusters_KMeans(mobile_scale, max_clusters = 10,
                                   initializer = "random",
                                   criterion = "WCSSE",
                                   plot_clusters = T)
mobile_km = KMeans_rcpp(mobile_scale, clusters = 3, num_init = 5,
                        max_iters = 200, initializer = "random")
mobile_km$WCSS_per_cluster
mobile_km_out <- as.data.frame(mobile_km$clusters) # cluster 2 is the largest cluster
#mobile_final <- cbind(mobile, mobile_km_out)
fviz_cluster(list(data=mobile_scale, cluster=mobile_km$clusters))
```
#### Changing K from 3 to 5
```{r}
mobile_km2 = KMeans_rcpp(mobile_scale, clusters = 5, num_init = 5,
                        max_iters = 100, initializer = "random")
mobile_km2$WCSS_per_cluster
mobile_km_out2 <- as.data.frame(mobile_km2$clusters) # cluster 3 is the largest cluster
#mobile_final2 <- cbind(mobile, mobile_km_out2)
fviz_cluster(list(data=mobile_scale, cluster=mobile_km2$clusters))
```
#### Update model
```{r}
mobile_scale <- scale(mobile)
opt_mobile1=Optimal_Clusters_KMeans(mobile_scale, max_clusters = 10,
                                   initializer = "kmeans++",
                                   criterion = "WCSSE",
                                   plot_clusters = T)
mobile_km1 = KMeans_rcpp(mobile_scale, clusters = 3, num_init = 5,
                        max_iters = 250, initializer = "kmeans++")
mobile_km1$WCSS_per_cluster
mobile_km_out1 <- as.data.frame(mobile_km1$clusters)
mobile_final <- cbind(mobile, mobile_km_out1)
fviz_cluster(list(data=mobile_scale, cluster=mobile_km1$clusters))
```
#### Analysing largest cluster
```{r}
mobile_large <- mobile_final %>% filter(`mobile_km1$clusters`==3)
summary(mobile_large)
mobile_second <- mobile_final %>% filter(`mobile_km1$clusters`==1)
summary(mobile_second)
```




